\LARGE \bf Grasp Metric for Gaussian Proccess Implicit Surface Representation of Shape Uncertainity

### 2014-07-04 paper.tex
Added .gitignore for *.log.  Reformatted paper for one sentence per line.  Some minor typo corrections.  Added equation for f and implicit surface (that might be the wrong definition, check that).  Added first description for workspace instead of just a voxel grid (the real world isnt just a voxel grid, and thats what were modeling when grasping).

\section{Problem Definition}
Given a grasp $G$ on an object, we can define it by the following tuple $G = \lbrace c_1,...,c_m,n_1,...,n_m,z,\mu\rbrace$. We have a set $I$ of $m$ contacts on the object where $i \in I$ contact is located at $c_i$ with surface normal $n_i$. The object has a center of mass $z$ and friction coefficient $\mu$. We demonstrate that one can efficiently compute a close form distribution for $c_i$,$n_i$ and $z$. We note though that our metric assumes a given $\mu$. \\

 For the following derivations we use the following notation. $\theta(x) = \lbrace \mu(x),\Sigma(x) \rbrace$, hence $\theta(x)$ is a tuple consisting of the mean and covariance functions given by the trained GPIS. We further assume that the contacts on the gripper approach along a line of action: $x = \gamma(t): R \rightarrow R^n$. The line segment has endpoints $a,b$ that are defined as the start of the gripper and end of the voxel grid respectively, as shown in Fig. \ref{fig:line_of_action}.We also denote the level set function as $f(x): \mathbb{R}^N \rightarrow \mathbb{R}$

@@

\subsection{Distribution on Contact Points}: The probability along the line $\gamma(g)$ is given by the following:

\begin{equation}
P(f(\gamma(g))|\theta(\gamma(g))) = N(\mu_T,\Sigma_T)
\end{equation}

@@

where $h_{S(g)}$ is convex on $\mathbb{R}^6$. Observe that q is invariant under fixed translation of the grasp center and contact positions. Furthermore, let $\mathbb{B}(r) = \lbrace x \in \mathbb{R}^3 : ||x|| \leq r \rbrace$. Then q is Lipschitz continuous on grasps with $m$ contact points lying in the set $X = \lbrace (c_1,...,c_m,n_1,...,n_m,z) : (c_i-z) \in \mathbb{B}(r), n_i \in \mathbb{S}^2 \rbrace$ with a Lipschitz constant given by $L= (1+\mu)(1+r)$ and where the chose distance measure \\

$d(g,g') = \sum_i ||(c_i-z)-(c_i'-z')|| + \sum_i ||n_i - n_i'||$\\

>>>>

\section{Problem Definition}
Given a grasp $G$ on an object, we can define it by the following tuple $G = \lbrace c_1,...,c_m,n_1,...,n_m,z,\mu\rbrace$. We have a set $I$ of $m$ contacts on the object where $i \in I$ contact is located at $c_i$ with surface normal $n_i$.
The object has a center of mass $z$ and friction coefficient $\mu$.
We demonstrate that one can efficiently compute a closed form distribution for $c_i$,$n_i$ and $z$.
We note though that our metric assumes a given $\mu$. \\
% TODO: finish that thought

 For the following derivations we use the following notation.
 $\theta(x) = \lbrace \mu(x),\Sigma(x) \rbrace$, hence $\theta(x)$ is a tuple consisting of the mean and covariance functions given by the trained GPIS.
We further assume that the contacts on the gripper approach along a line of action: $x = \gamma(t): R \rightarrow R^d$.
% TODO: Michael, I changed this from voxel grid because we're modeling a continuous space not a voxel grid, the voxel grid willbe an artifact of our integration/sampling strategies.
We assume a bounded rectangular workspace.
The line segment has endpoints $a,b$ that are defined as the start of the gripper and the intersection of the line with the end of the workspace respectively, as shown in Fig.
 \ref{fig:line_of_action}.
 % TODO: Draw a box around the workspace to show that b intersects the end of the workspace and draw a gripper approaching from a.  Also make A and B lowercase in the figure.
 We also define the function $f(x): \mathbb{R}^d \rightarrow \mathbb{R}$ as $f(x) = \mu(x)$ and an implicit surface $\mathcal{S} = \{ x \ | \ f(x) = 0 \}$.
% TODO: Michael, did I fill this in correctly? It was left blank initially.

@@

\subsection{Distribution on Contact Points} The probability along the line $\gamma(g)$ is given by the following:

\begin{equation}
P(f(\gamma(g))|\theta(\gamma(g))) 
=
\mN(\mu_T,\Sigma_T)
\end{equation}

% TODO: What is T?

@@

where $h_{S(g)}$ is convex on $\mathbb{R}^6$.
Observe that q is invariant under fixed translation of the grasp center and contact positions.
Furthermore, let $\mathbb{B}(r) = \lbrace x \in \mathbb{R}^3 : ||x|| \leq r \rbrace$.
Then q is Lipschitz continuous on grasps with $m$ contact points lying in the set $X = \lbrace (c_1, \dots, c_m,n_1, \dots,n_m,z) : (c_i-z) \in \mathbb{B}(r), n_i \in \mathbb{S}^2 \rbrace$ with a Lipschitz constant given by $L= (1+\mu)(1+r)$ and where the chose distance measure

\[
  d(g,g') = \sum_i ||(c_i-z)-(c_i'-z')|| + \sum_i ||n_i - n_i'||.
\]
